\documentclass[char]{guildcamp4}
\begin{document}
\name{\cEncyclopedia{}}

\bigquote{``Idaville looked like many seaside towns on the outside. On the inside, however, it was different. Very different. No one, grown-up or child, got away with breaking the law in Idaville.''}{- Donald J. Sobol}

The reason for Idaville's low crime rate is, of course, you. Encyclopedia Brown. Only child of Idaville's Police Chief, only thirteen years old and already your father's most valuable resource. Whenever a crime is too hard for him, he'll mention it to the family over the dinner table, and you'll close your eyes for a minute, drawing on that massive brain of yours, and ask the single question that will unlock the case. You've even taken it upon yourself to open a detective agency for the local children, helping them solve their own little mysteries and ensuring that justice is done even on the smallest scale.

Aside from your mighy deductive abilities and voracious reading habits, you're also known for your kindness, respectful behavior, and clean-cut presentation. You're so wholesome that you'd be right at home in "Leave it to Beaver" or a Norman Rockwell painting. You're the pride of Idaville and what every parent there secretly wishes their child to be.

In short, it's the perfect cover.

You realized very young the sick irony of your situation. Your feats of detection, which so many around you consider amazing -- deducing who stole Timmy's wagon, or putting together the infantile puzzle of who stole the typewriter from the museum -- barely register on your intellect. Meanwhile, your very own father, the CHIEF of the actual POLICE, sees your comings and goings every day and never thinks to ask questions like "how did Encyclopedia make enough money to buy all that high-end computer equipment," or "how did Encyclopedia know about that multiple homicide at the meth lab two days before they found the bodies?" Sometimes you want to shake him by the shoulders and scream at him. "Why do you think there's so much crime in our tiny little town? Don't you see I run this place?"

But of course, that would be giving the game away. By your calculations, by the time you're twenty, you're going to be not only the world's most famous detective, but also its most powerful crime boss. You've gotten an early start on both, widely publicizing your triumphs of detection -- mostly frame jobs -- while beginning to assemble a massive criminal empire online, hacking computers, blackmailing, and making a fortune wheeling and dealing on the dark web.

There is one nagging problem. Recently, some of your shipments have been going missing. Previously reliable contacts haven't been returning your messages, or have outright gone missing. Perhaps most distressingly, a boy two states over whose identity you stole and have been using in some of your dealings was recently picked up by the police. It seems like somebody may be on your trail. And, if they've been able to penetrate this far into your defenses, it's probably somebody good.

This invitation to a detective's awards ceremony, with so many of the world's top detectives in attendance, is the perfect opportunity. For one thing, you can weaken the structure of the world's detective hierarchy, both to make room for yourself and to lessen the chances of ever being caught. You can sow strife and discord where you can, while making sure your reputation for uprightness remains spotless. Even better than creating some disagreements would be permanently taking out some of the sharper detectives in attendance, and you've brought some highly potent poison for just that reason. If you happen to find that one of them is behind your recent business troubles, well... that would be all the better.

Furthermore, you can continue to up your profile as a whiz-kid crime solver. You can endear yourself to some of the more gullible and higher-profile attendees. Winning the election for next year's honoree at your young age would be a real feather in your cap. Even better would be winning the prize money guaranteed to the person who discovers who sent that threatening letter to this year's honoree. You could, of course, try to find out who did it. But framing somebody might be more up your alley. Even better would be doing both -- find the perpetrator, let them know you'll turn them in if they commit the murder and use that piece of blackmail for the rest of your career, then set somebody inconvenient up for the fall and watch the sparks fly.

All in all, this is the kind of night you live for. 

\begin{itemz}[Goals]
	\item Win the prize for discovering the author of the threat... by any means necessary.
	\item Win the election to be next year's honoree... also by any means necessary.
	\item Find out who's on the trail of your activities and ensure they are either incarcerated or dead by the night's end.
	\item Ensure at least three attendees die by the end of the evening.
	\item Sow strife and discord while keeping your own reputation spotless and squeaky clean.
\end{itemz} 

\begin{contacts}
	\contact{\cMackey{}} - This year's honoree. Sources tell you \cMackey{\they} may not be as upstanding as \cMackey{\they} seems. \cMackey{They} might make a good ally. Then again, engineering \cMackey{\their} fall from grace might be fun if \cMackey{they}'s not too cooperative. Better feel \cMackey{\them}  out.
	\contact{\cHistorian{}} - An old academic youve persuaded to think of \cHistorian{themself} as your mentor. \cHistorian{they} thinks the world of you and is very protective. What a fool. Better keep up the charade, and when somebody threatens you you can rely on \cHistorian{them} to protect you.
	\contact{\cMarlowe{}} - A pathetic, failed drunk, probably more apt at waving \cMarlowe{their} little gun around than obtaining any facts. If somebody has to take the fall for something, you could probably do worse than \cMarlowe{them}.
	\contact{\cLisbet{}} - A virtual nobody. For some reason, \cHistorian{} has seen fit to take \cLisbet{them} under \cHistorian{their} wing. Maybe out of pity. She seems to lack basic social skills. The association does not reflect well on you. It would probably be better if \cLisbet{they} were out of the picture, and given \cLisbet{their} awkwardness it shouldn't be difficult to cause \cLisbet{them} problems.
	\contact{\cTeaLady{}} - A doddering old idiot that they still trot out from time to time for special events. Old people love kids, so probably you can recruit \cTeaLady{him} as a supporter for your candidacy.
\end{contacts}

\end{document}

