\documentclass[char]{guildcamp4}
\begin{document}
\name{\cLisbet{}}

\bigquote{``Everyone has secrets. It's just a matter of finding out what they are.''}{- The Girl with the Dragon Tattoo}

Your traumatic childhood in what the rest of the world considers an idyllic paradise has taught you never to take anything at face value, never to trust without good reason. You've been hurt and taken advantage of enough to be very wary of other people. You much prefer the company of books, records, and especially computers. It's a good thing you're a world-class computer hacker.

That's why you decided to become a digital investigator. For one thing, you don't have to talk to anyone in person for too long. In the world of meat and social conventions, you feel lost. People's intentions are a mystery to you, their words hard to decipher, even their expressions are bewildering. You think you know what feelings are, think you may even have them yourself... but others always respond to you as if you're some kind of robot, and for your part, they seem unpredictable and erratic. Online, nothing is hidden from you.

That's why the case you've been working on recently is so troubling to you. For months, you've been caught in a web of related investigations. A series of crimes that seem at first to be disconnected -- some wire fraud here, a murder there -- but that feel to you in some way to bear a similar mark, and a connection to a certain group of sellers of illegal goods and services on the dark web. You can trace them all back a certain amount, but you always seem to hit a dead end. Frankly, you've never had this much trouble with a case before, and it seems to you that the person or people responsible must be familiar with modern investigative techniques at the highest level.

When you got the invitation to attend this ceremony honoring some pompous police detective, you would have thrown it straight in the trash if not for a nagging feeling that one of the attendees might very well be behind this vexing series of crimes. So, you broke into the ceremony's website and installed some tracking software. Sure enough, within a few days the attendee information page was accessed from a computer from an IP range you had already determined to be compromised by the organization you were chasing.

There is almost nothing you hate more than parties and formal gatherings. One thing you do hate more, however, is when those in power take advantage of their positions to hurt the powerless. And that is almost certainly happening here. You're going to the party, all right. You're going to find the person or people involved in the dark web crime spree, but you're not going to stop there. If there's one rotten apple in this bunch, then the rest of them probably are as well. It's time to expose them all to each other, and to the world.

There's also another distressing rumour you've heard. Due to that oafish newspaper reporter you've helped on and off, your prestige is growing. This is something you never asked for or wanted. And yet, there's already talk of giving you special recognition at next year's event, or even making you the honoree. This cannot be allowed to happen. In fact, if things were to get much worse, even declining a regular invitation next year might cause even more attention to turn towards you. All in all, better make sure you aren't invited back. But, simply asking might make you look modest, or shy. You need to be kicked out, to make sure it's over and done with. Rudeness and social awkwardness is not your weakness, tonight. It is your greatest strength.

\begin{itemz}[Goals]
	\item Find out who's behind the untraceable dark web crimes you've been looking into.
	\item Find three instances of hypocrisy or corruption and immediately expose them to everybody.
	\item Have the other attendees sign a formal declaration un-inviting you from next year's proceedings while letting at most one other attendee know that that's what you actually want.
	\item Find somebody who has been wronged by another attendee and avenge what has been done to them.
\end{itemz} 

\begin{contacts}
	\contact{\cMackey{}} - This year's honoree. Your online digging strongly suggests \cMackey{\they} is extremely corrupt. Could \c{Mackey{}}  be the one you're looking for?
	\contact{\cHistorian{}} - A \cHistorian{man} after your own heart, \cHistorian{} spends most of \cHistorian{their} time in library stacks and museums, following trails from long ago. \cHistorian{He} took you under \cHistorian{his} wing when you were just starting, and you haven't forgotten. You have a warm place for \cHistorian{him} in your heart, which you can't say for many people, and \cHistorian{his} attendance at this ceremony is one of the few things you're looking forward to, as you haven't seen in other in person in many years. So long, in fact, that you've begun to wonder if some things in his life might have changed... his involvement in cyber crime, for example.
	\contact{\cMarlowe{}} - \cMarlowe{He} has very little online presence, almost as if \cMarlowe{he} were living a life from fifty or sixty years ago. Or as if \cMarlowe{he} were covering \cMarlowe{his} tracks very, very carefully.
	\contact{\cEncyclopedia{}} - An alleged child prodigy. On the one hand, you feel an urge to take \cEncyclopedia{him} under your wing and help save \cEncyclopedia{him} from some fo the things you had to go through when you were young. On the other hand, children these days know a whole lot about the internet... and can anyone really be as squeaky clean as all that?
	\contact{\cTeaLady{}} Most people would probably think of \cTeaLady{him} as a harmless old \cTeaLady{man}, but you know better than to judge a book by its cover. You've seen the elderly get up to some very nasty business indeed. And the older a criminal in disguise gets, the wilier they must be...
\end{contacts}

\end{document}

