\documentclass[char]{GC2019}
\parindent=0pt
\begin{document}
\name{\cMAC{}}

Hi I am \cPM{\intro}.
You've always had something on someone ever since you're a little kid. You're the guy who sold cigarettes and stole people's lunches.You were the guy who found the English teacher and the math teacher in a dark closet The first year in high school and blackmailed them to get four years of A's.
Your dad was a cop, your granddad was a cop, and you've always known what you wanted to do. It was a little tough getting into the academy,  but your dad knew that the supervisor had been getting a little on the side from a local drug dealer, and knew where the account was... Rules were bent and you came out with flying colors. 
You met some like-minded friends and pretty soon you were running the town. The local drug dealers were reporting to you, you knew all the snitches, You know what was happening on every corner? And who had every secret. And you've got files. Lots and lots of files.
Pretty much seems like you have something on everyone.  And in a recognition of your fine work You're about to receive an award! The mayor is going to give you a local neighborhood liaison of the decade medal. It's going to be an all the papers, and it's your launch to a political career.  3 years of making sure everybody straightens out here, and then it's chief of police! With unlimited potential for bribes, blackmail, and skullduggery. 
There's one problem. All the local gum shoes.  Some of them are pretty good and some of them are on your trail.  You figure if you can get them all to the award ceremony, You can get information and evidence on all of them to make sure that they don't let your secrets out of the bag. Because you have so many secrets...
How can you make sure they all come? What about if somebody threatened to murder you? They all want fame unfortunate they'll all come to figure it out. what if we offer to reward to find out who it was that was trying to murder you ? What if somebody was trying to murder you at the ceremony? What if they wrote a letter and sent it to the paper, threatening to kill you right then and there and a spectacular fashion? That would get extra press! And when you survive everyone would think you're amazing!  
There's only one problem: No ones threatened you yet. But you're not a person to let that type of thing stand in your way. You'll write the letter to yourself, and frame one of those bozos with the job! You know how to plant evidence, You know how to get people to say what you want them to say it'll be easy right? 
Maybe you'll even fake a murder attempt on yourself and get one of them put away!
\begin{itemz}[Goals]
Get one piece of incriminating evidence from every sucker who shows:
( As a bonus, shoot yourself why no one is looking and frame one of them for it) 
	\item 
	Badge: your badge lets you arrest people with evidence items. You can stop them for 5 minutes  for an inquiry. 
  incriminating evidence:  you have 2 items that make people look bad. 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
Eb: this kid  likes Murder. 
Lisbet: You know she's after encyclopedia Brown. She was awesome to furious databases that were probably illegal to find information on him. They're trying to blackmail each other why shouldn't you get in on the job? If you can get proof that she was on the dark web illegally looking for information on encyclopedia Brown maybe you can get her to do anything.
Philip Marlowe: The first case he ever took, he supposedly didn't close nor did he find the body. You know that's not true. He knows who murdered who and he covered it up. If you can prove he didn't turn in the murderer, You could get his license revoked. You could probably get him to do anything if you could threaten that.
	
  Tea drinking old lady: So sweet, so smart, so easy to manipulate. Her dear  departed husband was in the way once when you were trying to blackmail one of his co-workers into covering your tracks on a heist, and he had to go. and you can't let a crime like that hang on your head, somebody had to be framed for it. Who better then the cloistered wife being stifled by an controlling husband? No one's ever found out about it but if you let that information out they'll put her away forever. You can use that information to have her denounce somebody else for writing that letter. And once she has illegally collected that reward money,  she will be complicit  with you and you will have her.
  Professor guy:  This guy has a habit. A hard  habit. A dark habit. A cocaine habit. You already exposed him once and he lost his pussy university job, it is hot girlfriend the tea drinking old lady,  and I found little escapade that entertained you for an afternoon. But then he decided he was going to start a new career as a detective. You know he's still doing it and he's probably got it on him. If you could get some cocaine and prove it came from him, you'd have him for life this time. 
  \contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
